Ecological validity of detecting data fabrication in experimental studies.

### 2016-05-23 submission/manuscript.Rmd
Add variance analyses per study, in addition to the one over all studies.

  obs_sigma_sd <- sd(c(tilde_s2_1, tilde_s2_2, tilde_s2_3, tilde_s2_4))

  iter <- 100000
  s2 <- dat$anch_sd[dat$referrer == pp]^2
  n_min_1 <- dat$anch_n[dat$referrer == pp] - 1
  ms_w <- c(rep(ms_w_1, 4), rep(ms_w_2, 4),
            rep(ms_w_3, 4), rep(ms_w_4, 4))
  sim_sigma <- NULL

  for (z in 1:16)
  {
    sim_sigma <- cbind(sim_sigma, ((rchisq(n = iter, df = n_min_1[z]) *  s2[z]) / n_min_1[z]) / ms_w[z])
  }

  sim_sigma_sd <- apply(sim_sigma, 1, sd)

  dat$variance_sd_p[sel] <- sum(sim_sigma_sd < obs_sigma_sd) / iter

@@

  dat$gender_fish[sel] <- -2 * sum(log(1 - ((p_gender[p_gender > .05] - .05) / (1 - .05))))
  dat$gender_fish_df[sel] <- 2 * length(p_gender)
  dat$gender_fish_p[sel] <- pchisq(-2 * sum(log(1 - ((p_gender[p_gender > .05] - .05) / (1 - .05)))),
                                   df = 2 * length(p_gender),
                                   lower.tail = FALSE)

  p_interaction <- unique(dat$p_interaction[sel])
  dat$interaction_fish[sel] <- -2 * sum(log(1 - ((p_interaction[p_interaction > .05] - .05) / (1 - .05))))
  dat$interaction_fish_df[sel] <- 2 * length(p_interaction)
  dat$interaction_fish_p[sel] <- pchisq(-2 * sum(log(1 - ((p_interaction[p_interaction > .05] - .05) / (1 - .05)))),
                                        df = 2 * length(p_interaction),
                                        lower.tail = FALSE)
}

dat_summary <- dat[ , -which(names(dat) %in% c("study",
                                               "partgender",
                                               "anchoring",
                                               "anch_n",
                                               "anch_m",
                                               "anch_sd",
                                               "f_gender",
                                               "df1_gender",
                                               "df2_gender",
                                               "p_gender",
                                               "f_condition",
                                               "df1_condition",
                                               "df2_condition",
                                               "p_condition",
                                               "f_interaction",
                                               "df1_interaction",
                                               "df2_interaction",
                                               "p_interaction"))]
dat_summary <- dat_summary[!duplicated(dat_summary$referrer), ]
dat_summary$fish_combine <- -2 * (log(dat_summary$variance_sd_p) + log(dat_summary$gender_fish_p) + 
        log(dat_summary$interaction_fish_p))
dat_summary$fish_combine_p <- pchisq(q = dat_summary$fish_combine,
                                     df = 2 * 3, lower.tail = FALSE)

write.csv(dat_summary,
          'test.csv', row.names = FALSE)
```

>>>>

  obs_sigma_sd <- sd(c(tilde_s2_1, tilde_s2_2, tilde_s2_3, tilde_s2_4))
  # Add the sigma sd observed per study (NOT PREREGISTERED)
  # Nog wijzigen adhv mva opmerkingen
  obs_sigma_sd_study1 <- sd(tilde_s2_1)
  obs_sigma_sd_study2 <- sd(tilde_s2_2)
  obs_sigma_sd_study3 <- sd(tilde_s2_3)
  obs_sigma_sd_study4 <- sd(tilde_s2_4)

  iter <- 100000
  s2 <- dat$anch_sd[dat$referrer == pp]^2
  n_min_1 <- dat$anch_n[dat$referrer == pp] - 1
  sim_sigma <- NULL

  for (z in 1:16)
  {
    # Made a small error in the preregistration, so this now deviates.
    sim_sigma <- cbind(sim_sigma, rchisq(n = iter, df = n_min_1[z]) / n_min_1[z])
  }

  # Standardize the generated SDs based on the msW from the simulated values
  # Per study
  ms_w_1 <- apply(sim_sigma[,1:4], 1, function(x) sum(n_min_1[1:4] * x) / sum(n_min_1[1:4]))
  ms_w_2 <- apply(sim_sigma[,5:8], 1, function(x) sum(n_min_1[5:8] * x) / sum(n_min_1[5:8]))
  ms_w_3 <- apply(sim_sigma[,9:12], 1, function(x) sum(n_min_1[9:12] * x) / sum(n_min_1[9:12]))
  ms_w_4 <- apply(sim_sigma[,13:16], 1, function(x) sum(n_min_1[13:16] * x) / sum(n_min_1[13:16]))

  sim_sigma[,1:4] <- sim_sigma[,1:4] / ms_w_1
  sim_sigma[,5:8] <- sim_sigma[,5:8] / ms_w_2
  sim_sigma[,9:12] <- sim_sigma[,9:12] / ms_w_3
  sim_sigma[,13:16] <- sim_sigma[,13:16] / ms_w_4

  # Calculate the variance of the simulated sds
  sim_sigma_sd_overall <- apply(sim_sigma, 1, sd)
  sim_sigma_sd_study1 <- apply(sim_sigma[,1:4], 1, sd)
  sim_sigma_sd_study2 <- apply(sim_sigma[,5:8], 1, sd)
  sim_sigma_sd_study3 <- apply(sim_sigma[,9:12], 1, sd)
  sim_sigma_sd_study4 <- apply(sim_sigma[,13:16], 1, sd)

  # Calculate the p-value overall and per study
  dat$variance_sd_p_overall[sel] <- sum(sim_sigma_sd_overall < obs_sigma_sd) / iter
  dat$variance_sd_p_study1[sel] <- sum(sim_sigma_sd_study1 < obs_sigma_sd_study1) / iter
  dat$variance_sd_p_study2[sel] <- sum(sim_sigma_sd_study2 < obs_sigma_sd_study2) / iter
  dat$variance_sd_p_study3[sel] <- sum(sim_sigma_sd_study3 < obs_sigma_sd_study3) / iter
  dat$variance_sd_p_study4[sel] <- sum(sim_sigma_sd_study4 < obs_sigma_sd_study4) / iter

@@

  dat$gender_fish[sel] <- -2 * sum(log(1 - ((p_gender[p_gender > .05] - .05) / (1 - .05))))
  dat$gender_fish_df[sel] <- 2 * length(p_gender[p_gender > .05])
  dat$gender_fish_p[sel] <- pchisq(-2 * sum(log(1 - ((p_gender[p_gender > .05] - .05) / (1 - .05)))),
                                   df = 2 * length(p_gender[p_gender > .05]),
                                   lower.tail = FALSE)

  p_interaction <- unique(dat$p_interaction[sel])
  dat$interaction_fish[sel] <- -2 * sum(log(1 - ((p_interaction[p_interaction > .05] - .05) / (1 - .05))))
  dat$interaction_fish_df[sel] <- 2 * length(p_interaction[p_interaction > .05])
  dat$interaction_fish_p[sel] <- pchisq(-2 * sum(log(1 - ((p_interaction[p_interaction > .05] - .05) / (1 - .05)))),
                                        df = 2 * length(p_interaction[p_interaction > .05]),
                                        lower.tail = FALSE)

  # correct outcomes for those participants 
  # who fabricated significant gender effects
  if (pp == 'R_9XhjfXDjcchvSiF' | pp == 'R_3JEilrqcgWYTOkd')
  {
    dat$gender_fish[sel] <- NA
    dat$gender_fish_df[sel] <- NA
    dat$gender_fish_p[sel] <- NA

    dat$interaction_fish[sel] <- NA
    dat$interaction_fish_df[sel] <- NA
    dat$interaction_fish_p[sel] <- NA

  } 
}

dat_summary <- dat[ , -which(names(dat) %in% c("study",
                                               "partgender",
                                               "anchoring",
                                               "anch_n",
                                               "anch_m",
                                               "anch_sd",
                                               "f_gender",
                                               "df1_gender",
                                               "df2_gender",
                                               "p_gender",
                                               "f_condition",
                                               "df1_condition",
                                               "df2_condition",
                                               "p_condition",
                                               "f_interaction",
                                               "df1_interaction",
                                               "df2_interaction",
                                               "p_interaction"))]
dat_summary <- dat_summary[!duplicated(dat_summary$referrer), ]
dat_summary$fish_combine_3 <- -2 * (log(dat_summary$variance_sd_p_overall) + log(dat_summary$gender_fish_p) + 
                                      log(dat_summary$interaction_fish_p))
dat_summary$fish_combine_3_p <- pchisq(q = dat_summary$fish_combine_3,
                                       df = 2 * 3, lower.tail = FALSE)
dat_summary$fish_combine_6 <- -2 * (log(dat_summary$variance_sd_p_study1) +
                                      log(dat_summary$variance_sd_p_study2) + 
                                      log(dat_summary$variance_sd_p_study3) + 
                                      log(dat_summary$variance_sd_p_study4) +
                                      log(dat_summary$gender_fish_p) + 
                                      log(dat_summary$interaction_fish_p))
dat_summary$fish_combine_6_p <- pchisq(q = dat_summary$fish_combine_6,
                                       df = 2 * 6, lower.tail = FALSE)

write.csv(dat_summary,
          dat_summary_file, row.names = FALSE)
```
